Community-Conditioned Language Models

### 2021-05-14 paper/paper.tex
text

@@

We find that various communities exhibit widely varying levels of
linguistic complexity \ref{hyp:varying-complexity}, with perplexity
per-word ranging from less than 34 to more than 65 for the best model 
architecture.

>>>>

Finally, we note that, even though community-conditioning affects
perplexity very little overall, it provides large benefits in term of
the underlying Bayesian classifier. Indiscernibility is on average
TODO with a standard deviation of TODO. Roughly speaking, this means
that, while the linguistic variations does not allow our model to
pinpoint the originating community of a message, it can often
eliminate TODO (a percentatge?) of communities as possible locations
for it. Further more, the information gain provided by
community-conditioning is a good predictor of how specific the
community is.

@@

\jp{I propose that most of the following analysis should be spread between the relevant sections, and only have a tiny summary here + future work.}
We find that various communities exhibit widely varying levels of
linguistic complexity \ref{hyp:varying-complexity}, with perplexity
per-word ranging from less than 34 to more than 65 for the best model 
architecture.
